### 2022-06-02 main/chapter_2ljets.tex
add vrlow zjets alt figure

Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_crz_pre_post}
Figure~\ref{fig:2ljets_low_vrlow_pre_post}

@@

>>>>

Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_crz_pre_post}
Figure~\ref{fig:2ljets_vrlow_alt}
Figure~\ref{fig:2ljets_low_vrlow_pre_post}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow.pdf}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow_mg5.pdf}
\caption{}
\end{subfigure}
\caption[
Pre-fit yields in VR-Low with standard and alternative $\zjets$ simulations
]{%
Pre-fit yields in VR-Low with (a) standard and (b) alternative $\zjets$
simulations.
Errors are statistical.
}
\label{fig:2ljets_vrlow_alt}
\end{figure}
